Here is the LaTeX code for the resume:
\documentclass{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[table]{xcolor}
\usepackage{fontspec}
\usepackage{tikz}

\definecolor{primary}{HTML}{3498db}
\definecolor{secondary}{HTML}{455a64}
\definecolor{accent}{HTML}{8e44ad}

\setmainfont{Montserrat}
\setsansfont{Lato}

\titleformat{\section}[block]{\Large\bfseries\sffamily\color{primary}}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\large\sffamily\color{secondary}}{\thesubsection}{1em}{}

\begin{document}

\pagestyle{empty}

\begin{center}
{\Huge\bfseries\sffamily MAAHIR VOHRA}\\
\medskip
{\large\bfseries\sffamily maahir.vohra14@gmail.com | (908)-887-3205 | Hackettstown, NJ}
\end{center}

\section{Profile}
\begin{tikzpicture}[overlay, remember picture]
\fill[primary!20] (current page.north west) rectangle ([yshift=-1.5cm]current page.north east);
\end{tikzpicture}
Successful computer science student with experience in full stack development, backend engineering, and project management.

\section{Experience}
\begin{tikzpicture}[overlay, remember picture]
\fill[secondary!20] (current page.north west) rectangle ([yshift=-1.5cm]current page.north east);
\end{tikzpicture}

\subsection{Full Stack Engineer Intern \& Co-op}
Cambridge Associates, June 2024 - Dec 2024

\begin{itemize}[leftmargin=*, itemsep=0.5em]
\item Developed backend services in Java Spring Boot and UI components in React/TypeScript for a financial client portal serving 1,300+ users.
\item Resolved 25+ production issues, improved stability, and shipped 8 new features enhancing performance and scalability.
\item Participated in sprint planning, code reviews, and QA testing with cross-functional teams in an Agile environment.
\item Optimized data handling logic with concurrency considerations, emphasizing performance and low-latency responses.
\end{itemize}

\subsection{Backend Engineer Intern}
Medtronic, May 2023 - Aug 2023

\begin{itemize}[leftmargin=*, itemsep=0.5em]
\item Automated clinical data pipelines in Python using SQLAlchemy and error handling, reducing execution time from 20 minutes to seconds.
\item Created reusable scripts for bulk database operations and integrity checks; visualized metrics via Power BI dashboards.
\item Validated backend services through unit testing and debugging across Linux environments.
\item Improved data reliability and efficiency, saving $65,000+ annually.
\end{itemize}

\section{Skills}
\begin{tikzpicture}[overlay, remember picture]
\fill[accent!20] (current page.north west) rectangle ([yshift=-1.5cm]current page.north east);
\end{tikzpicture}

\begin{itemize}[leftmargin=*, itemsep=0.5em]
\item Programming languages: Python, Java, C, C++, JavaScript, TypeScript
\item Databases: SQL, MySQL, Oracle SQL, PostgreSQL
\item Frameworks: Spring Boot, ReactJS, Flask
\item Cloud platforms: AWS, GCP
\item Operating Systems: Linux, Windows, MacOS
\item Tools: Docker, Power BI, Jira, GitHub
\item Certifications: Lean Six Sigma - A3 Yellow Belt Certification
\item Other: Bash, Assembly, TensorFlow, PyTorch, pyodbc, Figma
\end{itemize}

\section{Education}
\begin{tikzpicture}[overlay, remember picture]
\fill[primary!20] (current page.north west) rectangle ([yshift=-1.5cm]current page.north east);
\end{tikzpicture}

\begin{itemize}[leftmargin=*, itemsep=0.5em]
\item Bachelor of Science in Computer Science, New Jersey Institute of Technology (NJIT), Fall 2025, GPA: 3.5
\item Associate of Science in Computer Science, County College of Morris (CCM), Fall 2022
\end{itemize}

\end{document}